---
title: "Used_Car_Prices"
author: "Laura Zhao & Karen Truong"
date: "2023-11-13"
output: html_document
---
# Create the regression model using labeled data

## Read the data set into UsedCarPrices.
```{r}
UsedCarData <- read.csv("train_4.csv")
```

## Ensure the data set has been correctly read.
```{r}
head(UsedCarData)
```

## Filter the data set - remove rows with values that do not correspond to the preferences.
```{r}
# Only keep rows that have owner type as first
UsedCarData <- subset(UsedCarData, UsedCarData$Owner_Type == "First")

head(UsedCarData)

```

## Create dummy variables for the Location variable.
```{r}
#Uncomment if you need to download the "fastDummies" package
#install.packages("fastDummies")
library(fastDummies)
data_with_dummies <- dummy_cols(UsedCarData, select_columns = "Location")
UsedCarData <- cbind(UsedCarData, data_with_dummies)
UsedCarData <- UsedCarData[16:39]

#Check to see if the process was completed correctly
head(UsedCarData)

```


## Create dummy variables for the Transmission and Fuel_Type variable.
```{r}
#Create dummy variables for the Transmission and Fuel_Type variable.
UsedCarData$Transmission <- factor(UsedCarData$Transmission, levels = c("Automatic", "Manual"), labels = c(0,1))
UsedCarData$Fuel_Type <- factor(UsedCarData$Fuel_Type, levels = c("Diesel", "Petrol"), labels = c(0,1))

#Check to see if the process was completed correctly
head(UsedCarData)
```


## Clean the data by removing characters and turning data into numerical values.
```{r}
#Remove characters from variables that have units stored in their values
UsedCarData$Mileage <- as.integer(gsub("[^0-9]", "", UsedCarData$Mileage))
UsedCarData$Engine <- as.integer(gsub("[^0-9]", "", UsedCarData$Engine))
UsedCarData$Power <- as.integer(gsub("[^0-9]", "", UsedCarData$Power))
UsedCarData$New_Price <- as.integer(gsub("[^0-9]", "", UsedCarData$New_Price))

#Turn dummy variables into integers
UsedCarData$Transmission = as.numeric(UsedCarData$Transmission) - 1
UsedCarData$Fuel_Type = as.numeric(UsedCarData$Fuel_Type) -1

#Check to see if the process was completed correctly
head(UsedCarData)
```

## Remove variables we won't use in our model.
```{r}
#These values are the same for every car in our current data set, so we can exclude it from the regression.
UsedCarData$Owner_Type <- NULL

#Remove the New_Price variable because there are too many null values which will impact our results.
UsedCarData$New_Price <- NULL

#Remove variables that won't be used in the linear regression
UsedCarData$Location <- NULL
UsedCarData$Name <- NULL

#Check to see if the process was completed correctly
head(UsedCarData)
```

## Remove predictor variables with high correlations.
```{r}
#Visualize the relationship between all the variables with a correlation matrix
library("corrplot")
corrplot(cor(UsedCarData[, 1:20]), method="number")
plot(UsedCarData[, 1:20])
plot(UsedCarData$Year, UsedCarData$Price, pch=20)
abline(lm(UsedCarData$Price ~ UsedCarData$Year))
abline(lm(UsedCarData$Price ~ UsedCarData$Year))
```
Since none of the variables need to be removed, we can proceed with the linear regression model.

## Create the regression model
```{r}
#Create the regression model
regModel <- lm(UsedCarData$Price ~ UsedCarData$Year + UsedCarData$Kilometers_Driven + UsedCarData$Mileage + UsedCarData$Engine + UsedCarData$Power + UsedCarData$Seats + UsedCarData$Location_Ahmedabad + UsedCarData$Location_Bangalore + UsedCarData$Location_Chennai + UsedCarData$Location_Coimbatore + UsedCarData$Location_Delhi + UsedCarData$Location_Hyderabad + UsedCarData$Location_Jaipur + UsedCarData$Location_Kochi + UsedCarData$Location_Kolkata + UsedCarData$Location_Mumbai + UsedCarData$Location_Pune + UsedCarData$Transmission + UsedCarData$Fuel_Type)

#Get the summary statistics
summary(regModel)
```
There are several insignificant variables.
Thus, we should rerun the model and remove these variables one by one to see if they still remain insignificant.


```{r}
#Start by removing the most insignificant values, which would be Location_Jaipur.
regModel <- lm(UsedCarData$Price ~ UsedCarData$Year + UsedCarData$Kilometers_Driven + UsedCarData$Mileage + UsedCarData$Engine + UsedCarData$Power + UsedCarData$Seats + UsedCarData$Location_Ahmedabad + UsedCarData$Location_Bangalore + UsedCarData$Location_Chennai + UsedCarData$Location_Coimbatore + UsedCarData$Location_Delhi + UsedCarData$Location_Hyderabad  + UsedCarData$Location_Kochi + UsedCarData$Location_Kolkata + UsedCarData$Location_Mumbai + UsedCarData$Location_Pune + UsedCarData$Transmission + UsedCarData$Fuel_Type)

#Get the summary statistics
summary(regModel)
```


```{r}
#Remove Location_Pune.
regModel <- lm(UsedCarData$Price ~ UsedCarData$Year + UsedCarData$Kilometers_Driven + UsedCarData$Mileage + UsedCarData$Engine + UsedCarData$Power + UsedCarData$Seats + UsedCarData$Location_Ahmedabad + UsedCarData$Location_Bangalore + UsedCarData$Location_Chennai + UsedCarData$Location_Coimbatore + UsedCarData$Location_Delhi + UsedCarData$Location_Hyderabad  + UsedCarData$Location_Kochi + UsedCarData$Location_Kolkata + UsedCarData$Location_Mumbai + UsedCarData$Transmission + UsedCarData$Fuel_Type)

#Get the summary statistics
summary(regModel)
```

```{r}
#Remove Location_Kochi
regModel <- lm(UsedCarData$Price ~ UsedCarData$Year + UsedCarData$Kilometers_Driven + UsedCarData$Mileage + UsedCarData$Engine + UsedCarData$Power + UsedCarData$Seats + UsedCarData$Location_Ahmedabad + UsedCarData$Location_Bangalore + UsedCarData$Location_Chennai + UsedCarData$Location_Coimbatore + UsedCarData$Location_Delhi + UsedCarData$Location_Hyderabad + UsedCarData$Location_Kolkata + UsedCarData$Location_Mumbai + UsedCarData$Transmission + UsedCarData$Fuel_Type)

#Get the summary statistics
summary(regModel)
```

```{r}
#Remove Location_Delhi
regModel <- lm(UsedCarData$Price ~ UsedCarData$Year + UsedCarData$Kilometers_Driven + UsedCarData$Mileage + UsedCarData$Engine + UsedCarData$Power + UsedCarData$Seats + UsedCarData$Location_Ahmedabad + UsedCarData$Location_Bangalore + UsedCarData$Location_Chennai + UsedCarData$Location_Coimbatore  + UsedCarData$Location_Hyderabad + UsedCarData$Location_Kolkata + UsedCarData$Location_Mumbai + UsedCarData$Transmission + UsedCarData$Fuel_Type)

#Get the summary statistics
summary(regModel)
```

```{r}
#Remove Location_Ahmedabad
regModel <- lm(UsedCarData$Price ~ UsedCarData$Year + UsedCarData$Kilometers_Driven + UsedCarData$Mileage + UsedCarData$Engine + UsedCarData$Power + UsedCarData$Seats + UsedCarData$Location_Bangalore + UsedCarData$Location_Chennai + UsedCarData$Location_Coimbatore  + UsedCarData$Location_Hyderabad + UsedCarData$Location_Kolkata + UsedCarData$Location_Mumbai + UsedCarData$Transmission + UsedCarData$Fuel_Type)

#Get the summary statistics
summary(regModel)
```

```{r}
#Remove Location_Mumbai
regModel <- lm(UsedCarData$Price ~ UsedCarData$Year + UsedCarData$Kilometers_Driven + UsedCarData$Mileage + UsedCarData$Engine + UsedCarData$Power + UsedCarData$Seats + UsedCarData$Location_Bangalore + UsedCarData$Location_Chennai + UsedCarData$Location_Coimbatore  + UsedCarData$Location_Hyderabad + UsedCarData$Location_Kolkata + UsedCarData$Transmission + UsedCarData$Fuel_Type)

#Get the summary statistics
summary(regModel)
```

```{r}
#Remove Kilometers_Driven
regModel <- lm(UsedCarData$Price ~ UsedCarData$Year + UsedCarData$Mileage + UsedCarData$Engine + UsedCarData$Power + UsedCarData$Seats + UsedCarData$Location_Bangalore + UsedCarData$Location_Chennai + UsedCarData$Location_Coimbatore  + UsedCarData$Location_Hyderabad + UsedCarData$Location_Kolkata + UsedCarData$Transmission + UsedCarData$Fuel_Type)

#Get the summary statistics
summary(regModel)
```

```{r}
#Remove Location_Chennai
regModel <- lm(UsedCarData$Price ~ UsedCarData$Year + UsedCarData$Mileage + UsedCarData$Engine + UsedCarData$Power + UsedCarData$Seats + UsedCarData$Location_Bangalore + UsedCarData$Location_Coimbatore  + UsedCarData$Location_Hyderabad + UsedCarData$Location_Kolkata + UsedCarData$Transmission + UsedCarData$Fuel_Type)

#Get the summary statistics
summary(regModel)
```

Now, all remaining variables are significant.

## Create testing and training sets
```{r}
#Get the number of data points in the data set
num_samples = dim(UsedCarData)[1]

#Set the training set size to 80%
sampling.rate = 0.8

#Randomly select which data points will be included in the data set
training <- sample(1:num_samples, sampling.rate * num_samples, replace=FALSE)

#Define the training set with the selected training data points
trainingSet <- subset(UsedCarData[training, ])

#The remaining data will form the testing set
testing <- setdiff(1:num_samples, training)

#Define the testing set with the selected testing data points
testingSet <- subset(UsedCarData[testing, ])

head(testingSet)
```

## Create predictions for used car prices.
```{r}
#Fit a model for the training set
regModel <- lm(Price ~ Year + Mileage + Engine + Power + Seats + Location_Bangalore + Location_Coimbatore  + Location_Hyderabad + Location_Kolkata + Transmission + Fuel_Type, data=trainingSet)

#Perform predictions for the testing set
predictions <- predict(regModel, testingSet)

#Display the results
head(predictions)
```
## Evaluate the model by calculating error.
```{r}
#Calculate mse and remove all empty values within the error vector
error = predictions - testingSet$Price
any(is.na(error))
mse <- mean(error^2, na.rm = TRUE)
mse

```

# Predict used car prices.
## Read in the unlabeled data to determine how well the model can react to and predict for new and unseen data
```{r}
#Read in the unlabeled data
unlabeledData <- read.csv("unlabeled.csv")

#Check that the data has been read in.
head(unlabeledData)
```
## Clean the data
```{r}
#Create dummy variables for the Location variable.
data_with_dummies <- dummy_cols(unlabeledData, select_columns = "Location")
unlabeledData <- cbind(unlabeledData, data_with_dummies)
# unlabeledData <- unlabeledData[16:39]

#Create dummy variables
unlabeledData$Transmission <- factor(unlabeledData$Transmission, levels = c("Automatic", "Manual"), labels = c(0,1))
unlabeledData$Fuel_Type <- factor(unlabeledData$Fuel_Type, levels = c("Diesel", "Petrol"), labels = c(0,1))

#Remove characters from variables that have units stored in their values
unlabeledData$Mileage <- as.integer(gsub("[^0-9]", "", unlabeledData$Mileage))
unlabeledData$Engine <- as.integer(gsub("[^0-9]", "", unlabeledData$Engine))
unlabeledData$Power <- as.integer(gsub("[^0-9]", "", unlabeledData$Power))

#Turn dummy variables into integers
unlabeledData$Transmission = as.numeric(unlabeledData$Transmission) - 1
unlabeledData$Fuel_Type = as.numeric(unlabeledData$Fuel_Type) - 1
#These values are the same for every car in our current data set, so we can exclude it from the regression.
unlabeledData$Owner_Type <- NULL

#Remove the New_Price variable because there are too many null values which will impact our results.
unlabeledData$New_Price <- NULL

#Remove variables that won't be used in the linear regression
unlabeledData$Location <- NULL
unlabeledData$Name <- NULL

# Check to see if the process was completed correctly
head(unlabeledData)
```

## Perform the prediction with the linear regression model
```{r}
#Perform predictions for the unlabeled set
predictionsOfPrice <- predict(regModel, unlabeledData)

#Display the results
head(predictions)
```
## Evaluate the model by calculating error.
```{r}
#Read in the unlabeled data answers
truth <- read.csv("unlabeled_answers.csv")

#Check that the data has been read in.
head(truth)
```

```{r}
#Calculate mse and remove all empty values within the error vector
error = predictionsOfPrice - truth$Price
any(is.na(error))
mse <- mean(error^2, na.rm = TRUE)
mse

```

